Msc Thesis Figures

### 2022-08-28 docs/msc_thesis_figures.Rmd
add new code

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
suppressPackageStartupMessages({
  library(vegan)
  library(dendextend)
  library(ggbiplot)
  library(ggnewscale)
  library(raster)
  library(sf)
  library(tidyverse)
  library(ggplot2)
  library(gganimate)
  library(transformr)
  library(animation)
  library(rasterVis)
  library(ggmap)
  library(gifski)
  library(gtools)
  library(fmsb)
  library(RColorBrewer)
  library(scales)
  library(ggradar)
  library(tidymodels)
  library(patchwork)
  library(ggplotify)
})

@@

# Results dir + mun and mrc shapefile
mun <- st_read("../data/mun/munic_SHP_clean.shp", quiet = TRUE)
mrc <- st_read("../data/raw/vector/mrc_SHP/mrc_polygone.shp",  quiet = TRUE)
mrc.mont <- mrc %>% filter(MRS_NM_REG=="Montérégie") 
mrc.mont.reproj <- st_transform(mrc.mont, crs = st_crs(mun))

@@

# results key
sce_code_vec <- 
  as.vector(t(outer(c("BAU-", "RR-", "CP-", "CPR-", "CPTR-"), 
                    c("Hist", "Base", "RCP8"), paste0)))
sce_code_vec_run <- 
  rep(c("BAU", "RR", "CP", "CPR", "CPTR"), each=3)

@@

```{r figure_1_model_1, message=FALSE,  warning=FALSE, out.width="100%", fig.cap="Connectivity change for species through time, 2010-2100"}
colors_sce <- 
  data.frame(sce = c("Baseline", "RCP85"), 
             color = c("#8DA0CB", "#800026"), stringsAsFactors = F)

@@

```{r figure_1_model_2, message=FALSE, warning=FALSE, out.width="100%", fig.cap="Connectivity change for species through time, 2010-2100"}
fig_1_static_chap_2 <- joined %>% 
  filter(climate != "none", chapter %in% c("none", "both", "chap_2")) %>% 
  group_by(scenarioId, species, iteration) %>% 
  group_modify(~mutate(.x , baseline = subset(.x, timestep == 2010)$sum_cur, 
                       the_diff = ((sum_cur-baseline)/baseline)*100 )) %>% 
  ggplot(aes(x=timestep, y=the_diff, col=climate)) +
  scale_color_manual(values = colors_sce$color,
                     labels = colors_sce$sce) +
  geom_smooth(aes(group = sce, linetype=code_run), alpha=0.5, method="loess") +
  scale_linetype_manual(values=c("solid", "dashed", "longdash", "dotted")) +
  facet_wrap(~species, scales = "fixed") +
  geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5) +
  geom_vline(xintercept = 2020, linetype = "dashed", color = "darkGreen", alpha = 0.5) +
  labs(y = "Current flow (% Change)",
       x = "Year",
       col = "Climate",
       linetype = "Run") +
  guides(col = guide_legend(ncol = 2, nrow=2), 
         linetype = guide_legend(nrow = 2, ncol=2, 
                                 override.aes = list(colour = 'black'))) +
  theme(legend.position = c(0.85, 0.15))+
  NULL
#fig_1_static_chap_2
ggsave(fig_1_static_chap_2, 
       filename = "../thesis/figures/connectivity_decrease_x5species_chap2.png", 
       width = the_width, height = the_height, dpi = the_dpi)
```

@@

hist_plot_origin <- histograms %>%
  filter(sce %in% c("TRUE", "sce_37")) %>% 
  filter(ts == 2) %>% 
  mutate(ts = ts*10+1990) %>% 
  mutate(ts = as.factor(ts)) %>% 
  ggplot(aes(x=bins, y=n, fill=sce, colour =sce)) + 
  geom_density(stat='identity', show.legend=T, alpha=0.3)+
  scale_fill_manual(values = bi_colors, name="Source", labels=c("Model", "Observation")) +
  scale_color_manual(values = bi_colors, name="Source", labels=c("Model", "Observation")) +
  facet_wrap(~species) +
  labs(x = "Flow intensity distribution (log)", 
       y = "") +
  theme(strip.text.y = element_text(angle=360, size=10, hjust = 0), 
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), 
        axis.text.y.left = element_blank(),
        axis.ticks.y.left = element_blank()) +
  NULL
#hist_plot_origin
ggsave("../thesis/figures/original_hists.png", hist_plot_origin,
       width = the_width, height = the_height, dpi = the_dpi)
```

@@

hist_plot_1 <- histograms %>% 
  mutate(ts = as.factor(ts)) %>% 
  filter(chapter %in% c('both', 'chap_1')) %>%  
  ggplot(aes(x=bins, y=n, group=ts)) + 
  geom_density(stat='identity', show.legend=T, aes(fill=factor(ts), color=factor(ts)), alpha=0.3)+
  facet_grid(code~species) +
  scale_fill_manual(values = bi_colors, 
                    labels = c("2010", "2100")) +
  scale_color_manual(values = bi_colors, 
                     labels = c("2010", "2100")) +
  labs(x = "Flow intensity distribution (log)", 
       y = "")+
  theme(strip.text.y = element_text(angle=360, size=10, hjust = 0), 
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), 
        axis.text.y.left = element_blank(),
        axis.ticks.y.left = element_blank(), 
        legend.position = c(0.95, 0.96)) +
  labs(color="Timestep", fill="Timestep") +
  NULL
#hist_plot_1
ggsave("../thesis/figures/hist_chap1.png", hist_plot_1, width = 18, height = 15)
```

@@

```{r hist_plot_2, message=FALSE, warning=FALSE, out.width="100%"}
hist_plot_2 <- histograms %>% 
  mutate(ts = as.factor(ts)) %>% 
  filter(chapter %in% c('chap_2')) %>%  
  ggplot(aes(x=bins, y=n, group=ts)) + 
  geom_density(stat='identity', aes(fill=factor(ts),  colour=factor(ts)), alpha=0.3)+
  facet_grid(code~species) +
  scale_fill_manual(values = bi_colors, 
                    labels = c("2010", "2100")) +
  scale_color_manual(values = bi_colors, 
                     labels = c("2010", "2100")) +
  labs(x = "Flow intensity distribution (log)", 
       y = "") +
  theme(strip.text.y = element_text(angle=360, size=10, hjust = 0), 
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), 
        axis.text.y.left = element_blank(),
        axis.ticks.y.left = element_blank(),
        legend.position = c(0.95, 0.96)) +
  labs(color="Timestep", fill="Timestep") +
  NULL
#hist_plot_2
ggsave("../thesis/figures/hist_chap2.png", hist_plot_2, width = 18, height = 20)
```

@@

@@

```{r compare, eval=!(REPRO_FIGS_ONLY), message=FALSE, warning=FALSE, out.width="100%"}
source('../scripts/functions/draw_scenario.R')
for (scenario in c(39, 42, 45, 48, 51)){
  the_plot <- draw_scenario(scenario, mxp = mxp)
  the_name <- paste0("scenario_", as.character(scenario),"_compare.png")
  ggsave(plot = the_plot, 
         filename = paste0("../thesis/figures/",the_name), width = 30, height = 12, dpi = the_dpi)
}
```

@@

### Networks
##### CHAP 1
```{r, message=FALSE, warning=FALSE, out.width="100%", fig.cap=""}
networks <- read_csv("../outputs/final/final_df_network_stats.csv") %>% 
  left_join(results_clean, by = c("scenario" = "scenarioId"))

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
suppressPackageStartupMessages({
  library(vegan)
  library(dendextend)
  library(ggbiplot)
  library(ggnewscale)
  library(raster)
  library(sf)
  library(tidyverse)
  library(ggplot2)
  library(gganimate)
  library(transformr)
  library(animation)
  library(rasterVis)
  library(ggmap)
  library(gifski)
  library(gtools)
  library(fmsb)
  library(RColorBrewer)
  library(scales)
  library(ggradar)
  library(tidymodels)
  library(patchwork)
  library(ggplotify)
  library(gt)
  library(webshot)
  library(wesanderson)
  library(cowplot)
})

@@

# Results dir + mun and mrc shapefile
# mun <- st_read("../data/mun/munic_SHP_clean.shp", quiet = TRUE)
# mrc <- st_read("../data/raw/vector/mrc_SHP/mrc_polygone.shp",  quiet = TRUE)
# mrc.mont <- mrc %>% filter(MRS_NM_REG=="Montérégie") 
# mrc.mont.reproj <- st_transform(mrc.mont, crs = st_crs(mun))

@@

# results key
sce_code_vec <- 
  as.vector(t(outer(c("BAU-", "BAUR-", "CP-", "CPR-", "CPTR-"), 
                    c("Hist", "Base", "RCP8"), paste0)))
sce_code_vec_run <- 
  rep(c("BAU", "BAUR", "CP", "CPR", "CPTR"), each=3)

@@

```{r figure_1_model_1, message=FALSE,  warning=FALSE, out.width="100%", fig.cap="Connectivity change for species through time, 2010-2100"}

colors_sce <- 
  data.frame(sce = c("Baseline", "RCP85"), 
             color = c("#8DA0CB", "#800026"), stringsAsFactors = F)

@@

```{r figure_1_model_2, message=FALSE, warning=FALSE, out.width="100%", fig.cap="Connectivity change for species through time, 2010-2100"}
fig_1_static_chap_2 <- joined %>% 
  filter(climate != "none", chapter %in% c("none", "both", "chap_2")) %>% 
  group_by(scenarioId, species, iteration) %>% 
  group_modify(~mutate(.x , baseline = subset(.x, timestep == 2010)$sum_cur, 
                       the_diff = ((sum_cur-baseline)/baseline)*100 )) %>% 
  ggplot(aes(x=timestep, y=the_diff, col=climate)) +
  scale_color_manual(values = colors_sce$color,
                     labels = colors_sce$sce) +
  geom_smooth(aes(group = sce, linetype=code_run), alpha=0.5, method="loess") +
  scale_linetype_manual(values=c("solid", "dashed", "longdash", "dotted")) +
  facet_wrap(~species, scales = "fixed") +
  geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5) +
  geom_vline(xintercept = 2020, linetype = "dashed", color = "darkGreen", alpha = 0.5) +
  labs(y = "Current flow (% Change)",
       x = "Year",
       col = "Climate",
       linetype = "Run") +
  guides(col = guide_legend(ncol = 2, nrow=2), 
         linetype = guide_legend(nrow = 2, ncol=2, 
                                 override.aes = list(colour = 'black'))) +
  theme(legend.position = c(0.85, 0.15))+
  NULL
#fig_1_static_chap_2
ggsave(fig_1_static_chap_2, 
       filename = "../thesis/figures/connectivity_decrease_x5species_chap2.png", 
       width = the_width, height = the_height, dpi = the_dpi)
fig_1_static_chap_2
```

@@

hist_plot_origin <- histograms %>%
  filter(sce %in% c("TRUE", "sce_37")) %>% 
  filter(ts == 2) %>% 
  mutate(ts = ts*10+1990) %>% 
  mutate(ts = as.factor(ts)) %>% 
  ggplot(aes(x=bins, y=n, fill=sce, colour =sce)) + 
  geom_density(stat='identity', show.legend=T, alpha=0.3)+
  scale_fill_manual(values = bi_colors, name="Source", labels=c("Model", "Observation")) +
  scale_color_manual(values = bi_colors, name="Source", labels=c("Model", "Observation")) +
  facet_wrap(~species) +
  labs(x = "Flow intensity distribution (log)", 
       y = "") +
  theme(strip.text.y = element_text(angle=360, size=10, hjust = 0), 
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), 
        axis.text.y.left = element_blank(),
        axis.ticks.y.left = element_blank()) +
  NULL
#hist_plot_origin
ggsave("../thesis/figures/original_hists.png", hist_plot_origin,
       width = the_width, height = the_height, dpi = the_dpi)

hist_plot_origin
```

@@

hist_plot_1 <- histograms %>% 
  mutate(ts = as.factor(ts)) %>% 
  filter(chapter %in% c('both', 'chap_1')) %>%  
  filter(climate != "baseline") %>% 
  ggplot(aes(x=bins, y=n, group=ts)) + 
  geom_density(stat='identity', show.legend=T, aes(fill=factor(ts), color=factor(ts)), alpha=0.3)+
  facet_grid(code~species) +
  scale_fill_manual(values = bi_colors, 
                    labels = c("2010", "2100")) +
  scale_color_manual(values = bi_colors, 
                     labels = c("2010", "2100")) +
  labs(x = "Flow intensity distribution (log)", 
       y = "")+
  theme(strip.text.y = element_text(angle=360, size=20, hjust = 0), 
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), 
        axis.text.y.left = element_blank(),
        axis.ticks.y.left = element_blank(), 
        legend.position = c(0.94, 0.94)) +
  labs(color="Timestep", fill="Timestep") +
  NULL
#hist_plot_1
ggsave("../thesis/figures/hist_chap1.png", hist_plot_1, width = 18, height = 15)
hist_plot_1
```

@@

```{r hist_plot_2, message=FALSE, warning=FALSE, out.width="100%"}
hist_plot_2 <- histograms %>% 
  mutate(ts = as.factor(ts)) %>% 
  filter(chapter %in% c('chap_2')) %>%  
  filter(climate != "baseline") %>% 
  ggplot(aes(x=bins, y=n, group=ts)) + 
  geom_density(stat='identity', aes(fill=factor(ts),  colour=factor(ts)), alpha=0.3)+
  facet_grid(species~code) +
  scale_fill_manual(values = bi_colors, 
                    labels = c("2010", "2100")) +
  scale_color_manual(values = bi_colors, 
                     labels = c("2010", "2100")) +
  labs(x = "Flow intensity distribution (log)", 
       y = "") +
  theme(strip.text.y = element_text(angle=360, size=10, hjust = 0), 
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), 
        axis.text.y.left = element_blank(),
        axis.ticks.y.left = element_blank(),
        legend.position = c(0.94, 0.94)) +
  labs(color="Timestep", fill="Timestep") +
  NULL
#hist_plot_2
ggsave("../thesis/figures/hist_chap2.png", hist_plot_2, width = 18, height = 20)

hist_plot_2
```

@@

#### BOTH
```{r hist_plot_3, message=FALSE, warning=FALSE, out.width="100%"}
wes_2_colors = wes_palette("Zissou1", 2, type = "continuous")
hist_plot_3 <- histograms %>% 
  mutate(ts = as.factor(ts)) %>%

  filter(chapter %in% c('both', 'chap_1', 'chap_2')) %>%  
  filter(climate != "baseline") %>%

  ggplot(aes(x=bins, y=n, group=ts)) + 
  geom_density(stat='identity', aes(colour=factor(ts)), alpha=0.3)+
  facet_grid(code~species) +
  # scale_fill_manual(values = wes_2_colors, 
  #                   labels = c("2010", "2100")) +
  scale_color_manual(values = wes_2_colors, 
                     labels = c("2010", "2100")) +
  labs(x = "Flow intensity distribution (log)", 
       y = "") +
  theme(strip.text.y = element_text(angle=360, size=25, hjust = 0), 
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), 
        axis.text.y.left = element_blank(),
        axis.ticks.y.left = element_blank(),
        legend.position = c(0.94, 0.94)) +
  labs(color="Timestep") +
  NULL
#hist_plot_2
ggsave("../thesis/figures/hist_both_chap.png", hist_plot_3, width = 18, height = 15)

hist_plot_3
```

@@

```{r compare, eval=!(REPRO_FIGS_ONLY), message=FALSE, warning=FALSE, out.width="100%"}
source('../scripts/functions/draw_scenario.R')
mxp <- 1e10000 # 1000
the_dpi = 300
for (scenario in c(39, 42, 45, 48, 51)){
  the_plot <- draw_scenario(scenario, mxp = mxp, sce_folder = "/media/vlucet/backup/results_july/monteregie-conncons-scripted.ssim.output/")
  the_name <- paste0("scenario_", as.character(scenario),"_compare.png")
  ggsave(plot = the_plot,
  filename = paste0("../thesis/figures/",the_name), width = 15, height = 18, dpi = the_dpi)
}
```

@@

### Networks
```{r, message=FALSE, warning=FALSE, out.width="100%", fig.cap=""}
networks <- read_csv("../outputs/final/final_df_network_stats.csv") %>% 
  left_join(results_clean, by = c("scenario" = "scenarioId"))
```

##### CHAP 1
```{r, message=FALSE, warning=FALSE, out.width="100%", fig.cap=""}
networks <- read_csv("../outputs/final/final_df_network_stats.csv") %>% 
  left_join(results_clean, by = c("scenario" = "scenarioId"))

@@

```{r}
networks %>% 
  filter(scenario != 37, timestep %in% c(2,10)) %>% 
  filter(species %in% c("MAAM", "URAM")) %>% 
  pivot_longer(numNodes:overallECnatal, names_to = "metric", values_to = "values") %>% 
  select (species, iteration, timestep, code_run, climate, metric, values) %>% 
  group_by(species, timestep, code_run, climate, metric) %>% 
  summarise(values = mean(values)) %>% 
  ungroup() %>% 
  pivot_wider(names_from = timestep, names_glue = "ts_{timestep}_{.value}", values_from = values) %>% 
  mutate(percent_change = (ts_10_values - ts_2_values)/ts_2_values) %>% 
  select(-starts_with("ts")) %>% 
  pivot_wider(names_from = metric, values_from = percent_change) %>% 
  mutate(code_run = fct_relevel(code_run, c("BAU", "BAUR", "CP", "CPR", "CPTR"))) %>% 
  arrange(code_run) %>% 
  mutate(climate = fct_relevel(climate, c("baseline", "RCP 8.5")))  %>% 
  arrange(code_run, climate) %>% 
  mutate(scenario = paste(code_run, climate)) %>%
  arrange(code_run, climate, scenario) %>% 
  select(-c(code_run, climate)) %>%
  select(species, scenario, starts_with("overall"), numNodes, numLinks, meanAreaQuality, meanCost) %>%

  gt(rowname_col = "scenario", groupname_col = "species") %>% 
  fmt_percent(everything()) %>% 
  cols_label(
    overallECgap = "EC (gap)", 
    overallECnatal = "EC (natal)", 
    numNodes = "Nodes", 
    numLinks = "Links", 
    meanAreaQuality = "Mean Quality", 
    meanCost = "Mean Cost"
  ) %>% 
  data_color(
    columns = overallECgap:meanAreaQuality, 
    colors = scales::col_bin(palette = as.character(paletteer::paletteer_c("scico::cork", n = 100)), 
                             bins = seq(from =-1, to = 1, by = 0.1))) %>% 
  data_color(
    columns = meanCost, 
    colors = scales::col_bin(palette = as.character(paletteer::paletteer_c("scico::cork", n = 100)), 
                             bins = seq(from =-1, to = 1, by = 0.1), reverse = -1)) -> metrics_table 
metrics_table
gtsave(metrics_table, "../thesis/figures/metrics.png")

```{r}
networks_tbl <- networks
# networks_tbl$code_run[networks_tbl$code_run == "BAUR"] <- "\n    BAUR"
# networks_tbl$code_run[networks_tbl$code_run == "CP"] <- "    CP"
# networks_tbl$code_run[networks_tbl$climate == "RCP 8.5"] <- "RCP 8.5"
networks_tbl %>% 
  filter(scenario != 37, timestep %in% c(2,10)) %>% 
  # filter(species %in% c("MAAM", "URAM")) %>% 
  pivot_longer(numNodes:overallECnatal, names_to = "metric", values_to = "values") %>% 
  select (species, iteration, timestep, code_run, climate, metric, values) %>% 
  group_by(species, timestep, code_run, climate, metric) %>% 
  summarise(values = mean(values)) %>% 
  ungroup() %>% 
  pivot_wider(names_from = timestep, names_glue = "ts_{timestep}_{.value}", values_from = values) %>% 
  mutate(percent_change = (ts_10_values - ts_2_values)/ts_2_values) %>% 
  select(-starts_with("ts")) %>%

  # pivot_wider(names_from = metric, values_from = percent_change) %>%

  mutate(code_run = fct_relevel(code_run, c("BAU", "BAUR", "CP", "CPR", "CPTR"))) %>% 
  arrange(code_run) %>% 
  mutate(climate = fct_relevel(climate, c("baseline", "RCP 8.5")))  %>% 
  arrange(code_run, climate) %>% 
  mutate(scenario = paste(code_run, climate)) %>%
  arrange(code_run, climate, scenario) %>%

  select(-c(code_run, climate)) %>%

  pivot_wider(names_from = "scenario", values_from = "percent_change") %>%

  # select(species, scenario, starts_with("overall"), numNodes, numLinks, meanAreaQuality, meanCost) %>% 
  filter(metric %in% c("overallECgap", "overallECnatal", "numNodes", 
                       "numLinks", "meanAreaQuality")) %>%

  # mutate(metric = fct_relevel(metric, c("overallECgap", "overallECnatal", "numNodes", 
  #                                       "numLinks", "meanAreaQuality"))) %>% 
  left_join(data.frame(metric = c("overallECgap", "overallECnatal", "numNodes", 
                                  "numLinks", "meanAreaQuality"), 
                       metric_name = c("EC (gap)", "EC (natal)", "Nodes", 
                                       "Links", "Quality"))) %>% 
  mutate(metric_name = fct_relevel(metric_name, c("EC (gap)", "EC (natal)", "Nodes", 
                                                  "Links", "Quality"))) %>%
  arrange(metric_name) %>%
  select(-metric) %>%

  gt(rowname_col = "metric_name", groupname_col = "species") %>% 
  fmt_percent(everything(), decimals=0) %>% 
  data_color(
    columns = `BAU baseline`:`CPTR RCP 8.5`, 
    colors = scales::col_bin(palette = as.character(paletteer::paletteer_c("scico::cork", n = 100)), 
                             bins = seq(from =-1, to = 1, by = 0.1))) %>%
  tab_options(data_row.padding = px(1)) %>% 
  cols_width(metric_name~px(89), everything()~px(68)) %>% 
  tab_style(locations = cells_body(), cell_text(size = 12)) -> metrics_table_2 # %>% # 89
# data_color(
#   columns = meanCost, 
#   colors = scales::col_bin(palette = as.character(paletteer::paletteer_c("scico::cork", n = 100)), 
#                            bins = seq(from =-1, to = 1, by = 0.1), reverse = -1))

metrics_table_2
gtsave(metrics_table_2, "../thesis/figures/metrics_2.png")

```{r}
URAM <- networks %>% 
  filter(scenario != 37, timestep %in% c(2,10)) %>% 
  pivot_longer(numNodes:overallECnatal, names_to = "metric", values_to = "values") %>% 
  select (species, iteration, timestep, code_run, climate, metric, values) %>% 
  group_by(species, timestep, code_run, climate, metric) %>% 
  summarise(values = mean(values)) %>% 
  ungroup() %>% 
  pivot_wider(names_from = timestep, names_glue = "ts_{timestep}_{.value}", values_from = values) %>% 
  mutate(percent_change = (ts_10_values - ts_2_values)/ts_2_values*100) %>% 
  select(-starts_with("ts")) %>% 
  mutate(code_run = fct_relevel(code_run, c("BAU", "BAUR", "CP", "CPR", "CPTR"))) %>% 
  arrange(code_run) %>% 
  mutate(climate = fct_relevel(climate, c("baseline", "RCP 8.5")))  %>% 
  arrange(code_run, climate) %>% 
  mutate(scenario = paste(code_run, climate)) %>%
  arrange(code_run, climate, scenario) %>%

  select(-c(code_run, climate)) %>% 
  ungroup() %>% 
  filter(species == "URAM") %>% 
  filter(metric %in% c("overallECgap", "overallECnatal", "numNodes", 
                       "numLinks", "meanAreaQuality")) %>% 
  left_join(data.frame(metric = c("overallECgap", "overallECnatal", "numNodes", 
                                  "numLinks", "meanAreaQuality"), 
                       metric_name = c("EC (gap)", "EC (natal)", "Nodes", 
                                       "Links", "Quality"))) %>% 
  mutate(metric_name = fct_relevel(metric_name, c("EC (gap)", "EC (natal)", "Nodes", 
                                                  "Links", "Quality"))) %>%
  arrange(metric_name) %>%
  select(-metric) %>% 
  mutate(`% Change` = percent_change, Metric = metric_name, Scenario = scenario) %>% 
  tidyHeatmap::heatmap(Scenario, Metric, `% Change`, .scale="none", cluster_columns = FALSE)

BLBR <- networks %>% 
  filter(scenario != 37, timestep %in% c(2,10)) %>% 
  pivot_longer(numNodes:overallECnatal, names_to = "metric", values_to = "values") %>% 
  select (species, iteration, timestep, code_run, climate, metric, values) %>% 
  group_by(species, timestep, code_run, climate, metric) %>% 
  summarise(values = mean(values)) %>% 
  ungroup() %>% 
  pivot_wider(names_from = timestep, names_glue = "ts_{timestep}_{.value}", values_from = values) %>% 
  mutate(percent_change = (ts_10_values - ts_2_values)/ts_2_values*100) %>% 
  select(-starts_with("ts")) %>% 
  mutate(code_run = fct_relevel(code_run, c("BAU", "BAUR", "CP", "CPR", "CPTR"))) %>% 
  arrange(code_run) %>% 
  mutate(climate = fct_relevel(climate, c("baseline", "RCP 8.5")))  %>% 
  arrange(code_run, climate) %>% 
  mutate(scenario = paste(code_run, climate)) %>%
  arrange(code_run, climate, scenario) %>%

  select(-c(code_run, climate)) %>% 
  ungroup() %>% 
  filter(species == "BLBR") %>% 
  filter(metric %in% c("overallECgap", "overallECnatal", "numNodes", 
                       "numLinks", "meanAreaQuality")) %>% 
  left_join(data.frame(metric = c("overallECgap", "overallECnatal", "numNodes", 
                                  "numLinks", "meanAreaQuality"), 
                       metric_name = c("EC (gap)", "EC (natal)", "Nodes", 
                                       "Links", "Quality"))) %>% 
  mutate(metric_name = fct_relevel(metric_name, c("EC (gap)", "EC (natal)", "Nodes", 
                                                  "Links", "Quality"))) %>%
  arrange(metric_name) %>%
  select(-metric) %>% 
  mutate(`% Change` = percent_change, Metric = metric_name, Scenario = scenario) %>% 
  tidyHeatmap::heatmap(Scenario, Metric, `% Change`, .scale="none", cluster_columns = FALSE)

MAAM <- networks %>% 
  filter(scenario != 37, timestep %in% c(2,10)) %>% 
  pivot_longer(numNodes:overallECnatal, names_to = "metric", values_to = "values") %>% 
  select (species, iteration, timestep, code_run, climate, metric, values) %>% 
  group_by(species, timestep, code_run, climate, metric) %>% 
  summarise(values = mean(values)) %>% 
  ungroup() %>% 
  pivot_wider(names_from = timestep, names_glue = "ts_{timestep}_{.value}", values_from = values) %>% 
  mutate(percent_change = (ts_10_values - ts_2_values)/ts_2_values*100) %>% 
  select(-starts_with("ts")) %>% 
  mutate(code_run = fct_relevel(code_run, c("BAU", "BAUR", "CP", "CPR", "CPTR"))) %>% 
  arrange(code_run) %>% 
  mutate(climate = fct_relevel(climate, c("baseline", "RCP 8.5")))  %>% 
  arrange(code_run, climate) %>% 
  mutate(scenario = paste(code_run, climate)) %>%
  arrange(code_run, climate, scenario) %>%

  select(-c(code_run, climate)) %>% 
  ungroup() %>% 
  filter(species == "MAAM") %>% 
  filter(metric %in% c("overallECgap", "overallECnatal", "numNodes", 
                       "numLinks", "meanAreaQuality")) %>% 
  left_join(data.frame(metric = c("overallECgap", "overallECnatal", "numNodes", 
                                  "numLinks", "meanAreaQuality"), 
                       metric_name = c("EC (gap)", "EC (natal)", "Nodes", 
                                       "Links", "Quality"))) %>% 
  mutate(metric_name = fct_relevel(metric_name, c("EC (gap)", "EC (natal)", "Nodes", 
                                                  "Links", "Quality"))) %>%
  arrange(metric_name) %>%
  select(-metric) %>% 
  mutate(`% Change` = percent_change, Metric = metric_name, Scenario = scenario) %>% 
  tidyHeatmap::heatmap(Scenario, Metric, `% Change`, .scale="none", cluster_columns = FALSE)

PLCI <- networks %>% 
  filter(scenario != 37, timestep %in% c(2,10)) %>% 
  pivot_longer(numNodes:overallECnatal, names_to = "metric", values_to = "values") %>% 
  select (species, iteration, timestep, code_run, climate, metric, values) %>% 
  group_by(species, timestep, code_run, climate, metric) %>% 
  summarise(values = mean(values)) %>% 
  ungroup() %>% 
  pivot_wider(names_from = timestep, names_glue = "ts_{timestep}_{.value}", values_from = values) %>% 
  mutate(percent_change = (ts_10_values - ts_2_values)/ts_2_values*100) %>% 
  select(-starts_with("ts")) %>% 
  mutate(code_run = fct_relevel(code_run, c("BAU", "BAUR", "CP", "CPR", "CPTR"))) %>% 
  arrange(code_run) %>% 
  mutate(climate = fct_relevel(climate, c("baseline", "RCP 8.5")))  %>% 
  arrange(code_run, climate) %>% 
  mutate(scenario = paste(code_run, climate)) %>%
  arrange(code_run, climate, scenario) %>%

  select(-c(code_run, climate)) %>% 
  ungroup() %>% 
  filter(species == "PLCI") %>% 
  filter(metric %in% c("overallECgap", "overallECnatal", "numNodes", 
                       "numLinks", "meanAreaQuality")) %>% 
  left_join(data.frame(metric = c("overallECgap", "overallECnatal", "numNodes", 
                                  "numLinks", "meanAreaQuality"), 
                       metric_name = c("EC (gap)", "EC (natal)", "Nodes", 
                                       "Links", "Quality"))) %>% 
  mutate(metric_name = fct_relevel(metric_name, c("EC (gap)", "EC (natal)", "Nodes", 
                                                  "Links", "Quality"))) %>%
  arrange(metric_name) %>%
  select(-metric) %>% 
  mutate(`% Change` = percent_change, Metric = metric_name, Scenario = scenario) %>% 
  tidyHeatmap::heatmap(Scenario, Metric, `% Change`, .scale="none", cluster_columns = FALSE)

RASY <- networks %>% 
  filter(scenario != 37, timestep %in% c(2,10)) %>% 
  pivot_longer(numNodes:overallECnatal, names_to = "metric", values_to = "values") %>% 
  select (species, iteration, timestep, code_run, climate, metric, values) %>% 
  group_by(species, timestep, code_run, climate, metric) %>% 
  summarise(values = mean(values)) %>% 
  ungroup() %>% 
  pivot_wider(names_from = timestep, names_glue = "ts_{timestep}_{.value}", values_from = values) %>% 
  mutate(percent_change = (ts_10_values - ts_2_values)/ts_2_values*100) %>% 
  select(-starts_with("ts")) %>% 
  mutate(code_run = fct_relevel(code_run, c("BAU", "BAUR", "CP", "CPR", "CPTR"))) %>% 
  arrange(code_run) %>% 
  mutate(climate = fct_relevel(climate, c("baseline", "RCP 8.5")))  %>% 
  arrange(code_run, climate) %>% 
  mutate(scenario = paste(code_run, climate)) %>%
  arrange(code_run, climate, scenario) %>%

  select(-c(code_run, climate)) %>% 
  ungroup() %>% 
  filter(species == "RASY") %>% 
  filter(metric %in% c("overallECgap", "overallECnatal", "numNodes", 
                       "numLinks", "meanAreaQuality")) %>% 
  left_join(data.frame(metric = c("overallECgap", "overallECnatal", "numNodes", 
                                  "numLinks", "meanAreaQuality"), 
                       metric_name = c("EC (gap)", "EC (natal)", "Nodes", 
                                       "Links", "Quality"))) %>% 
  mutate(metric_name = fct_relevel(metric_name, c("EC (gap)", "EC (natal)", "Nodes", 
                                                  "Links", "Quality"))) %>%
  arrange(metric_name) %>%
  select(-metric) %>% 
  mutate(`% Change` = percent_change, Metric = metric_name, Scenario = scenario) %>% 
  tidyHeatmap::heatmap(Scenario, Metric, `% Change`, .scale="none", cluster_columns = FALSE)
```

```{r}
mtcars_tidy <- 
  mtcars %>% 
  as_tibble(rownames="Car name") %>% 
  mutate_at(vars(-`Car name`, -hp, -vs), scale) %>%
  pivot_longer(cols = -c(`Car name`, hp, vs), names_to = "Property", values_to = "Value")
mtcars_tidy_nested <- bind_rows(mutate(mtcars_tidy, Year=1990), mutate(mtcars_tidy, Year=2000)) %>% 
  mutate(Value = runif(n = n(), min = 0, max = 10))
mtcars_tidy_nested %>% 
  heatmap(`Car name`, Property, Value) 
```

#### HEATMAP

```{r}
HEATMAP_data <- networks %>% 
  filter(scenario != 37, timestep %in% c(2,10)) %>% 
  pivot_longer(numNodes:overallECnatal, names_to = "metric", values_to = "values") %>% 
  select (species, iteration, timestep, code_run, climate, metric, values) %>% 
  group_by(species, timestep, code_run, climate, metric) %>% 
  summarise(values = mean(values)) %>% 
  ungroup() %>% 
  pivot_wider(names_from = timestep, names_glue = "ts_{timestep}_{.value}", values_from = values) %>% 
  mutate(percent_change = (ts_10_values - ts_2_values)/ts_2_values*100) %>% 
  select(-starts_with("ts")) %>% 
  mutate(code_run = fct_relevel(code_run, c("BAU", "BAUR", "CP", "CPR", "CPTR"))) %>% 
  arrange(code_run) %>% 
  mutate(climate = fct_relevel(climate, c("baseline", "RCP 8.5")))  %>% 
  arrange(code_run, climate) %>% 
  mutate(scenario = paste(code_run, climate)) %>%
  arrange(code_run, climate, scenario) %>%

  select(-c(code_run, climate)) %>% 
  ungroup() %>% 
  #filter(species == "URAM") %>% 
  filter(metric %in% c("overallECgap", "overallECnatal", "numNodes", 
                       "numLinks", "meanAreaQuality")) %>% 
  left_join(data.frame(metric = c("overallECgap", "overallECnatal", "numNodes", 
                                  "numLinks", "meanAreaQuality"), 
                       metric_name = c("EC (gap)", "EC (natal)", "Nodes", 
                                       "Links", "Quality"))) %>% 
  mutate(metric_name = fct_relevel(metric_name, c("EC (gap)", "EC (natal)", "Nodes",
                                                  "Links", "Quality"))) %>%
  arrange(metric_name) %>%
  select(-metric) %>% 
  mutate(`% Change` = percent_change, `Connectivity Metric` = metric_name, `Species / Scenario` = scenario) %>% 
  select(species, `% Change`, `Connectivity Metric`, `Species / Scenario`)

titles <- expand_grid(left = c("BAU", "BAUR", "CP", "CPR", "CPTR"), right = c("baseline", "RCP 8.5")) %>% mutate(final = paste(left, right)) %>% pull(final) %>% sort()
